DeepSphere: an efficient graph-based spherical CNN

### 2019-09-04 main.tex
fix quotes
title

\title{Which spherical CNN should you use?\\ DeepSphere V2}

@@

batch size 32, adam optimizer, constant learning rate of $5 \cdot 10^{-2}$
cross-entropy loss, and add triplet loss from ``Esteves et al.´´

@@

concat the results of the corresponding encoder layer after the graph convolution. Similar to ``Jiang et al.´´
\subsubsection*{Equiangular}
Equiangular sampling, with a latitude bandwidth 384 and longitude bandwidth 576.

@@

\begin{dmath}
    [GC_{50}\, +\, BN\, +\, ReLU]\, +\, [GC_{100}\, +\, BN\, +\, ReLU]\, +\, [GC_{100}\, +\, BN\, +\, ReLU]\, +\, GAP\, +\, FCN
\end{dmath}
\end{document}

>>>>

%\title{Which spherical CNN should you use?\\ DeepSphere V2}
\title{DeepSphere: an efficient graph-based spherical CNN}
%\title{DeepSphere, an efficient (& equivariant) graph-based spherical CNN}

@@

batch size 32, adam optimizer, constant learning rate of $5 \cdot 10^{-2}$
cross-entropy loss, and add triplet loss from ``Esteves et al.''

@@

concat the results of the corresponding encoder layer after the graph convolution. Similar to ``Jiang et al.''
\subsubsection*{Equiangular}
Equiangular sampling, with a latitude bandwidth 384 and longitude bandwidth 576.

@@

\begin{dmath}
    [GC_{50}\, +\, BN\, +\, ReLU]\, +\, [GC_{100}\, +\, BN\, +\, ReLU]\, +\, [GC_{100}\, +\, BN\, +\, ReLU]\, +\, GAP\, +\, FCN
\end{dmath}

\end{document}
